Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-03-15 analysis/paper/paper.Rmd
Add severity rating figure
Will need to be adapted for publication, but will work for now for drafting article

Disease scoring was the same in both experiments using a sheath blight assessment scale for field evaluation developed at IRRI. Two sample areas per plot (1m x 1m) were assessed. for 9 hills per sample, the number of tillers per hill and number of tillers with sheath blight (incidence) were measured. Tiller sheath blight severity was measured for four tillers per hill and six leaves tiller. Five and four disease assessments were made in 2015 and 2016, respectively.

>>>>

Disease scoring was the same in both experiments using a sheath blight assessment scale for field evaluation developed at IRRI \ref{figure1}. Two sample areas per plot (1m x 1m) were assessed. for 9 hills per sample, the number of tillers per hill and number of tillers with sheath blight (incidence) were measured. Tiller sheath blight severity was measured for four tillers per hill and six leaves tiller. Five and four disease assessments were made in 2015 and 2016, respectively.

![IRRI sheath blight field severity rating scale where, 0 - 0%, 1 - 1%, 2 - 5%,
3 - 15%, 4 - 50%, 5 - >50%. \label{figure1}](./Figures/Figure 1 IRRI Sheath Blight Severity Assessment.png)
